%
% Copyright (C) 2017 Jan Nowotsch
% Author Jan Nowotsch	<jan.nowotsch@gmail.com>
%
% Released under the terms of the GNU GPL v2.0
%



\chapter{Architecture Abstraction\label{chap:arch}}
	The architecture interface implements an abstraction layer for the actual target hardware. It provides the interface between the target hardware and the kernel, cf. Chapter~\ref{chap:kernel}.


\section{Interface Header}
	\begin{description}
	\item[include/arch/arch.h]
		\hyperref[arch_8h]{include/arch/arch.h} is the main architecture header file. It provides access to the architecture implementation defined through \lstinline{CONFIG_ARCH_HEADER}. The header includes the respective architecture header and provides macros to call kernel and common functions as well as a macro to access architecture information. Therefor, it also defines the types containing the architecture interface callback functions, which are \hyperref[structarch__ops__kernel__t]{arch\_ops\_kernel\_t} for kernel and \hyperref[structarch__ops__common__t]{arch\_ops\_common\_t} for common callbacks.

	\item[include/arch/*]
		The remaining header files in \lstinline{include/arch} contain wrapper macros to access all of the architecture interface functions separately.
	\end{description}


\section{Defining an Architecture}
	The following is required to implement support for a target architecture.

	\subsection{Types}
		\begin{itemize}
			\item \lstinline{struct thread_ctx_t}: struct to store the processor context
		\end{itemize}

	\subsection{Constants}
		\begin{itemize}
			\item \lstinline{ARCH_NUM_INTS}: number of hardware interrupts
		\end{itemize}

	\subsection{Callback Functions}
		The callback functions are registers by defining variables of type \hyperref[structarch__ops__kernel__t]{arch\_ops\_kernel\_t} and \hyperref[structarch__ops__common__t]{arch\_ops\_common\_t} named \lstinline{arch_ops_kernel} and \lstinline{arch_ops_common}. Further, in order to get access to the architecture specific data, a variable of type \lstinline{arch_info_t}, named \lstinline{arch_info} needs to be declared.

	\subsection{Interrupt Handling and Nesting}
		The architecture layer is responsible for handling all interrupts and passing control to the kernel where necessary, e.g. for system calls and timer interrupts. For all interrupts that pass control to the kernel, the interrupted thread's context needs to be saved properly and stored to the currently running thread, cf. \hyperref[kernel_2sched_8c_a34a33397e7197f803feffb423ce6717a]{sched\_running()}. That is, such interrupts may be used as preemption points and cause the active thread to switch.

		In general the architecture layer may decide on interrupt nesting. However, in most cases it should be sufficient to let the kernel decide.

		Further, the architecture interrupt implementation is responsible to:
		\begin{enumerate}
			\item preserve the kernel \hyperref[errno_8h_ad65a8842cc674e3ddf69355898c0ecbf]{errno} variable
			\item reset \hyperref[errno_8h_ad65a8842cc674e3ddf69355898c0ecbf]{errno} before passing control to kernel handlers
		\end{enumerate}

	\subsection{System Calls}
		The system call implementation is required to:
		\begin{enumerate}
			\item kernel: update the errno member of \hyperref[sys_2syscall_8h_structsc__arg__t]{sc\_arg\_t}
			\item user space: update \hyperref[errno_8h_ad65a8842cc674e3ddf69355898c0ecbf]{errno}
		\end{enumerate}

	\subsection{Kconfig}
		\begin{itemize}
			\item respective \quote{Processor type} has to be added
			\item the following CONFIG-variables need to be defined
				\begin{itemize}
					\item \lstinline{CONFIG_ARCH}
					\item \lstinline{CONFIG_PROCESSOR}
					\item \lstinline{CONFIG_ADDR_WIDTH.*}
					\item \lstinline{CONFIG_REGISTER_WIDTH.*}
					\item \lstinline{CONFIG_ARCH_HEADER}
				\end{itemize}
		\end{itemize}

	\subsection{Build System}
		\begin{itemize}
			\item libsys.o shall containing all objects that are required to be linked against applications
			\item linker script scripts/linker/kernel\_$<$arch$>$.lds
			\item memory layout print (optional): scripts/memlayout/main.c, if target specific sections are required
				\begin{itemize}
					\item mandatory memory sections shall be printed using \lstinline{PRINT_RANGE_EE}
					\item optional memory sections shall be printed using \lstinline{PRINT_RANGE}
				\end{itemize}

			\item memory layout check: scripts/memlayout/check.c, if target specific sections shall be checked add them to the \lstinline{regs} array.
		\end{itemize}

\vfill
\pagebreak
\input{arch/avr}
